Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-09 Thesis/chapter/03-theoretical-background.tex
comment Swann1988 sputtering

\subsection{Zirconium oxide}
Zirconium oxide \td{(Zr02)} is ceramic with a bandgap of 5-7 eV and dielectric constant of 15-22\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \td{PV} industry. 
It is monoclinic below 1170 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C. \td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
what is important properites of zro2?

\subsection{Sputtering}
% https://en.wikipedia.org/wiki/Sputter_deposition
\td{what is the principle behind sputtering
what is sputtering, how does it work, what different kinds of sputtering is there, 
what is is used for? 
what was it used for in this work? 
}
%Sputtering is a physical deposition method. 
Sputtering describes the process of particles being sputtered from a surface after 
impact of highly energetic particles.
These high energy particles start cascades of momentum transfers. 
If a path of a cascade reaches back to the surface and the kinetic energy of a surface 
particle exceeds the binding energy, it is ejected (or sputtered).

>>>>

\subsection{Zirconium oxide}
Zirconium oxide \td{(ZrO2)} is ceramic with a bandgap of 5-7 eV and dielectric constant of 15-22\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \td{PV} industry. 
It is monoclinic below 1170 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Stevens1986}.
%\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
\td{what is important properites of zro2? }

\subsection{Sputtering}
% https://en.wikipedia.org/wiki/Sputter_deposition
\td{what is the principle behind sputtering
what is sputtering, how does it work, what different kinds of sputtering is there, 
what is is used for? 
what was it used for in this work? 
}
\td{
- phenomon of high energy particle bombardement know off particles from a source\\
- options to create high energy particles: electron gun, thermal evaporation or cathode? 
- vorteile sind: Swann p 67(2)
- need low pressure bcs of MFP but plasma needs gas to sustain
- source is target and target is substrate

}
%Sputtering is a physical deposition method. 
Sputtering describes the process of particles being sputtered from a surface after 
impact of highly energetic particles.
These high energy particles start cascades of momentum transfers. 
If a path of a cascade reaches back to the surface and the kinetic energy of a surface 
particle exceeds the binding energy, it is ejected (or sputtered).
